SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-24 2017-Xudong-SMT/ActaInformatica.tex
Draft proof of Th.2 and Th.3.

@@

@@

\begin{figure}[ht]
\centerline{ 
  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1-aut}
  \hspace{25mm}
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2-aut}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a1}_P \},\\ [\forall x1. a1\neq\delta(x1)]}
    {A_0 \xrightarrow{a1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x2)}_P,\,
                            \xrightarrow{acc(x2)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x2)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a3}_q \},\\ [\forall x3. a3\neq\delta(x3)] }
    {A_1 \xrightarrow{a3} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b1}_P\}, ~~ [\forall y1. b1\neq\delta(y1) \!\land\! v=0]}
    {B_0 \xrightarrow{b1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(y2)}_P,\,
                            \xrightarrow{acc(y2)}_Q \}, \\
                                        v=0, \\
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(y2)}} B_1}\\
    ot'_3  =& \openrule{
                            \xrightarrow{b2}_q, \\ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
    {B_1 \xrightarrow{b2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}

>>>>

\begin{proof}

Intuitively, $\forall \ostate{\tilde{s}}\in\textit{Explored}=State(L)\text{, there must exist a transition}\ostate{\tilde{s_i}}\xrightarrow{v_i}\ostate{\tilde{s}}\text{ and }\forall \ostate{\tilde{s}}\in\textit{Explored}_{Smart}=State(L_{Smart})\text{, }\exists\ostate{\tilde{pre(s)}}\text{, }\ostate{\tilde{pre(s)}}\xrightarrow{v}\ostate{\tilde{s}}\text{ where \textit{Pred} is satisfiable and the state}\ostate{\tilde{pre(s)}}\text{ has two cases:}$
\begin{enumerate}
	\item[(1)] $\ostate{\tilde{pre(s)}}=\ostate{\tilde{s}}$
	\item[(2)] $\ostate{\tilde{pre(s)}}\in\textit{Explored}\text{-}\{\ostate{\tilde{s}}\}$
\end{enumerate}
By induction, there must exists a sequence $\ostate{\tilde{s_0}}\xrightarrow{v_i}\ostate{\tilde{s}}$ where all the $\textit{Pred}_i$ are satisfiable.

Then $\forall\ostate{\tilde{t}}\textit{Explored}=State(L)$, there are also two cases:
\begin{enumerate}
	\item[(1)] $\ostate{\tilde{t}}\in State(L1)$

	By definition of reachability, there exists a sequence $\ostate{\tilde{s_0}}...\xrightarrow{v_j}...\ostate{\tilde{t}}$ where all the $\textit{Pred}_j$ are satisfiable.

	$\Rightarrow \ostate{\tilde{t}}\in State(L_{Smart})$
	\item[(2)] $\ostate{\tilde{t}}\in State(L)\text{-}State(L1)$, then $\forall \ostate{\tilde{u}}\in\textit{Explored}-\{\ostate{\tilde{t}}\}$,
	\begin{enumerate}
		\item[(1)] $\ostate{\tilde{u}}\in State(L)\text{-}State(L1)$.
		\item[(2)] $\ostate{\tilde{u}}\in State(L1)$, but there is no transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$.
		\item[(3)] $\ostate{\tilde{u}}\in State(L1)$, there exists transition $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{t}}$, but the $\textit{Pred}_u$ is unsatisfiable.
	\end{enumerate}
	By induction, there is no sequence from $\ostate{\tilde{s_0}}$ to $\ostate{\tilde{t}}$.

	$\Rightarrow \ostate{\tilde{t}}\notin State(L_{Smart})$
\end{enumerate}
Overall, $State(L1)$ is equal to $State(L_{Smart})$.
\end{proof}

@@

\begin{proof}
In Theorem 2, we have already proved the result set of global states of two algorithm are the same without the assignments.

If there exists assignments in the open transitions.

In Algorithm 3, $\forall\ostate{\tilde{t}}\notin State(L_{Smart})$, if there is a transition $\ostate{\tilde{t}}\xrightarrow{v_t}\ostate{\tilde{t'}}$ contains an assignment $\textit{Post}_t$, and in following transitions $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$, we need to check $\textit{Pred}\and\bigwedge\textit{Post}_i$ where $\textit{Post}_i \notin \{\textit{Post}_t\}$.

In Algorithm 1, the same state $\ostate{\tilde{t}}\notin State(L1)$, also has a transition $\ostate{\tilde{t}}\xrightarrow{v_t}\ostate{\tilde{t'}}$ contains an assignment $\textit{Post}_t$, and in following transitions $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$, what need to check is $\textit{Pred}\and\bigwedge\textit{Post}_i$.
As $b_1\and b_2\rightarrow b_1$, if $\ostate{\tilde{u}}\xrightarrow{v_u}\ostate{\tilde{u'}}$ exists in the result of Algorithm 3, it is also contained in the original result.

After the final reachability computation, $\{\textit{Post}_t\}$ is removed from $\{\textit{Post}_i\}$ then the assertions to check become the same, then the transitions of the result are also the same. So the result open automaton of Algorithm 3 is exactly the same as that of  Algorithm 1.
\end{proof}

@@

\begin{figure}[ht]
\centerline{ 
  \includegraphics[width=0.30\linewidth]{ActaXFIG/Enable1}
  \hspace{25mm}
  \includegraphics[width=0.25\linewidth]{ActaXFIG/Enable2}}
  \begin{minipage}{5.7cm}
$  \begin{array}{@{}r@{}l@{}}
    ot_1  = &\openrule{\{ \xrightarrow{a1}_P \},\\ [\forall x1. a1\neq\delta(x1)]}
    {A_0 \xrightarrow{a1} A_0}\\
    ot_2  =& \openrule{
                            \{\xrightarrow{\delta(x2)}_P,\,
                            \xrightarrow{acc(x2)}_Q\}  }
    {A_0 \xrightarrow{\underline{\delta(x2)}} A_1}\\
    ot_3  =& \openrule{
                          \{  \xrightarrow{a3}_q \},\\ [\forall x3. a3\neq\delta(x3)] }
    {A_1 \xrightarrow{a3} A_1}
  \end{array}$
  \end{minipage}
  \hspace{2mm}
  \begin{minipage}{6cm}
$  \begin{array}{@{}r@{}l@{}}
    ot'_1  =& \openrule{
    	\{\xrightarrow{b1}_P\}, ~~ [\forall y1. b1\neq\delta(y1) \!\land\! v=0]}
    {B_0 \xrightarrow{b1} B_0}\\
    ot'_2  =& \openrule{
                            \{\xrightarrow{\delta(y2)}_P,\,
                            \xrightarrow{acc(y2)}_Q \}, \\
                                        v=0, \\
                                        \{v\gets 1\}}
    {B_0 \xrightarrow{\underline{\delta(y2)}} B_1}\\
    ot'_3  =& \openrule{
                            \xrightarrow{b2}_q, \\ [\forall y2. b2\neq\delta(y2) \!\land\! v=1] }
    {B_1 \xrightarrow{b2} B_1}
  \end{array}$
  \end{minipage}
  \caption{The two open automata}
  \label{schema:enable-OAs}
\end{figure}
